%
% Copyright 2016 Erint Labs OÜ
%
% Licensed under the EUPL, Version 1.1 or – as soon they
% will be approved by the European Commission - subsequent
% versions of the EUPL (the "Licence");
% You may not use this work except in compliance with the
% Licence.
% You may obtain a copy of the Licence at:
%
% https://joinup.ec.europa.eu/software/page/eupl
%
% Unless required by applicable law or agreed to in
% writing, software distributed under the Licence is
% distributed on an "AS IS" basis,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either
% express or implied.
% See the Licence for the specific language governing
% permissions and limitations under the Licence.
%
\input{preamble}

% Neat box for votings
\newcommand\voteline[2]{#1:&\fieldwhs{#2}{30}{10}{8} \%\\}
\newcommand\votebox[4]{\begin{tabular}{r l}\voteline{#2}{#1yes}\voteline{#3}{#1no}\voteline{#4}{#1abs}\end{tabular}}
\newcommand\voteUK[1]{\votebox{#1UK}{За}{Проти}{Утрималось}}
\newcommand\voteEN[1]{\votebox{#1EN}{For}{Against}{Abstained}}
\newcommand\voteET[1]{\votebox{#1ET}{Poolt}{Vastu}{Erapooletuid}}

% TODO: generalise minutes template

\begin{document}
  \begin{Form}
    \title{Протокол зібрання вкладників / Shareholder meeting minutes / Osanike kooosoleku protokoll\\№ \fieldrws{minuteno}{6}{250}{14}}
    % TODO: using author field for place is ugly, let's use another docuement class in future
    \author{\fieldterm{placeUK} / \fieldterm{placeEN} / \fieldterm{placeET}}
    \date{\today / \textenglish{\today} / \textestonian{\today}}
    \maketitle
    \thispagestyle{fancy}

    \begin{paracol}{3}
      \clause % TODO do we have to support people who refused an ID number btw? Add this if necessary
        {Преамбула}
        {Preamble}
        {Preambul}
        { Назва суб’єкта господарювання:\\
          \fieldline{companynameUK}\\
          Реєстраційний код та країна:\\
          \fieldline{companycodeUK}\\
          Юридична адреса:\\
          \fieldline{companyaddress1UK}\\
          \fieldline{companyaddress2UK}\\
          Голова зібрання:\\
          \fieldline{chairmanUK}\\
          Секретар зібрання:\\
          \fieldline{secretaryUK}\\
          Мова зібрання:\\
          \fieldline{languageUK}
        }
        { Company name:\\
        \fieldline{companynameEN}\\
          Registry entry code and country:\\
          \fieldline{companycodeEN}\\
          Official seat:\\
          \fieldline{companyaddress1EN}\\
          \fieldline{companyaddress2EN}\\
          Minutes chairman:\\
          \fieldline{chairmanEN}\\
          Recording secretary:\\
          \fieldline{secretaryEN}\\
          Мinutes language:\\
          \fieldline{languageEN}
        }
        { Osaühingu ärinimi:\\
          \fieldline{companynameET}\\
          Osaühingu registrikood ja riik:\\
          \fieldline{companycodeET}\\
          Osaühingu asukoht:\\
          \fieldline{companyaddress1ET}\\
          \fieldline{companyaddress2ET}\\
          Koosoleku juhataja:\\
          \fieldline{chairmanET}\\
          Koosoleku protokollija:\\
          \fieldline{secretaryET}\\
          Koosoleku keel:\\
          \fieldline{languageET}
        }

      \clause
        {Кворум}
        {Quorum}
        {Kvoorum}
        {Зібрання відвідало \fieldw{participantsUK}{25} учасників (\smartref{app:attend}{додаток }), що представляють \fieldw{votesUK}{25}\% голосів. Отже, на Зібранні достягнуто кворуму.}
        {The meeting was attended by \fieldw{participantsEN}{25} participants (\smartref{app:attend}{appendix }), who represent \fieldw{votesEN}{25}\% of voting rights. Therefore the Meeting has reached a quorum.}
        {Koosolekul osales \fieldw{participantsET}{25} osalejat (\smartref{app:attend}{lisa }), kes esindavad \fieldw{votesET}{25}\% osadega esindatud häältest. Seega on Koosolekul olemas otsustusvõimeline kvoorum.}

      \clause
        {Порядок денний}
        {Agenda}
        {Päevakord}
        { \subsection{Припинення повноважень правління}
          Визнати нечинним поточний склад правління, ухвалений:\\
          \fieldline{previous1UK}\\
          \fieldline{previous2UK}\\
          датованому(-ій):\\
          \fieldline{previousdateUK}
          \subsection{Призначення нового складу правління}
          Призначити членами правління осіб, визначених у \smartref{app:management}{додатку }, безстроково з наступного календарного дня після дня проведення цього Зібрання.
          \subsection{Зміна назви компанії}
          Визнати \fieldw{name}{75} як нову назву компанії.
          \subsection{Зміна статутного капіталу}
          Призначити новий розмір статутного капіталу у розмірі \fieldw{capital}{75} €.
          \subsection{Перерозподіл долей в компанії}
          Перерозподілити долі в компанії у відповідності до \smartref{app:shares}{додатку }. Долі вважати переданими у дар.
        }
        { \subsection{Suspension of the management board}
          Suspend the current management board elected by:\\
          \fieldline{previous1EN}\\
          \fieldline{previous2EN}\\
          dated:\\
          \fieldline{previousdateEN}
          \subsection{Election to the new management board}
          Elect the persons indicated in the \smartref{app:management}{appendix } without a term starting from the next callendar day following the day of this Meeting.
          \subsection{Company name change}
          Acknowledge \fieldw{name}{75} as the new name for the company.
          \subsection{Legal capital change}
          Change the amount of the company's legal capital to \fieldw{capital}{75} €.
          \subsection{Company shares redistribution}
          Redistribute the shares of the company in accordance with \smartref{app:shares}{appendix }. Shares are to be considered gifted.
        }
        { \subsection{Osaühingu juhatuse laialisaatmine}
          Laiali saata praeguse juhatuse liikmed, kes valiti:\\
          \fieldline{previous1ET}\\
          \fieldline{previous2ET}\\
          dateeritud:\\
          \fieldline{previousdateET}
          \subsection{Uue juhatuse valimine}
          Valida \smartref{app:management}{liites } märgitud  tähtajatult alates Kooseleku päevale järgnevast kalendripäevast.
          \subsection{Osaühingu ärinime muutmine}
          Kinnitada \fieldw{name}{75} kui osaühingu uus nimi.
          \subsection{Osakapitali muutmine}
          Osaühingu osakapitali muutmine summas \fieldw{capital}{75} €.
          \subsection{Osaühingu osakute ümberjagamine}
          Osaühingu osakute ümberjagamine vastavalt \smartref{app:shares}{liites } väljatoodule. Osakuid käsitleda, kui kingitust.
        }
      \multibreak
      \clause
        {Рішення}
        {Resolutions}
        {Otsused}
        { \subsection{Припинення повноважень правління}
          \voteUK{suspend}
          \subsection{Призначення нового складу правління}
          \voteUK{appoint}
          \subsection{Зміна назви компанії}
          \voteUK{name}
          \subsection{Зміна статутного капіталу}
          \voteUK{capital}
          \subsection{Перерозподіл долей в компанії}
          \voteUK{shares}
        }
        { \subsection{Suspension of the management board}
          \voteEN{suspend}
          \subsection{Election to the new management board}
          \voteEN{appoint}
          \subsection{Company name change}
          \voteEN{name}
          \subsection{Legal capital change}
          \voteEN{capital}
          \subsection{Company shares redistribution}
          \voteEN{shares}
        }
        { \subsection{Juhatuse laialisaatmine}
          \voteET{suspend}
          \subsection{Uue juhatuse valimine}
          \voteET{appoint}
          \subsection{Osaühingu ärinime muutmine}
          \voteET{name}
          \subsection{Osakapitali muutmine}
          \voteET{capital}
          \subsection{Osaühingu osakapitali ümberjagamine}
          \voteET{shares}
        }

      \freetextnoindent
        {\\Рішення Зібрання прийняті у відповідності до закону та процедур прийняття рішень, зазначених у статуті Суб’єкта господарювання.}
        {\\The Meeting's decisions were adopted in compliance with the law and the decision making procedures indicated in the Company's articles of association.}
        {\\Koosolekul võeti otsused vastu järgides seadusi ja Osaühingu põhikirjas sätestatud otsuste vastuvõtmise korda.}

    \end{paracol}
  \appendix
  \section{На зібранні присутні\\The meeting was attended by\\Koosolekul osalesid}
  \label{app:attend}
  \newcounter{n}
  \setcounter{n}{35}
  \newcounter{i}
  \begin{tabular}{ | r | l | l | l | l | }
    \hline
      & Ім’я учасника (Кирилиця) &  Ім’я учасника (Латинка) & Ідентифікаційний номер та країна & Права голосу, \% \\
      & Participant's name (Cyrillic) & Participant's name (Latin) & Idetification number and country & Vote rights, \% \\
      № & Osaleja nimi (Kirillitsa) & Osaleja nimi (Ladina) & Isikukood ja Riik & Hääleõigus, \% \\
    \hline
      \setcounter{i}{0}
      \myloop{i}{n}{ \arabic{i} & \fieldtw{votercyr\arabic{i}}{150} &
                     \fieldtw{voterlat\arabic{i}}{150} &
                     \fieldtw{votercode\arabic{i}}{200} &
                     \fieldt{votervotes\arabic{i}} }
      \hline
  \end{tabular}
  \pagebreak
  \section{Новий склад правління\\The new management board\\Uue juhatuse}
  \label{app:management}
  \setcounter{n}{35}
  \begin{tabular}{ | r | l | l | l | l | }
    \hline
      & Ім’я особи (Кирилиця) &  Ім’я особи (Латинка) & Ідентифікаційний номер та країна & Дата народження \\
      & Person's name (Cyrillic) & Person's name (Latin) & Idetification number and country & Date of birth \\
      № & Isiku nimi (Kirillitsa) & Isiku nimi (Ladina) & Isikukood ja Riik & Sünnikuupäev \\
    \hline
      \setcounter{i}{0}
      \myloop{i}{n}{ \arabic{i} & \fieldtw{managercyr\arabic{i}}{150} &
                     \fieldtw{managerlat\arabic{i}}{150} &
                     \fieldtw{managercode\arabic{i}}{200} &
                     \fieldtw{managerdob\arabic{i}}{75} }
      \hline
  \end{tabular}
  \pagebreak
  \section{Новий розподіл долей в компанії\\The new distribution of company shares\\Koosolekul osalesid}
  \label{app:shares}
  \setcounter{n}{35}
  \begin{tabular}{ | r | l | l | l | l | }
    \hline
      & Ім’я учасника (Кирилиця) &  Ім’я учасника (Латинка) & Ідентифікаційний номер та країна & Доля, \% \\
      & Participant's name (Cyrillic) & Participant's name (Latin) & Idetification number and country & Share, \% \\
      № & Osaleja nimi (Kirillitsa) & Osaleja nimi (Ladina) & Isikukood ja Riik & Osas, \% \\
    \hline
      \setcounter{i}{0}
      \myloop{i}{n}{ \arabic{i} & \fieldtw{votercyr\arabic{i}}{150} &
                     \fieldtw{voterlat\arabic{i}}{150} &
                     \fieldtw{votercode\arabic{i}}{200} &
                     \fieldt{votervotes\arabic{i}} }
      \hline
  \end{tabular}
  \pagebreak
  \input{appendix_correspondence}
  \end{Form}
\end{document}
